---
output:
  html_document:
   # code_folding: hide
    toc: yes
    toc_collapse: no
    toc_float: yes
    theme: spacelab
    fig_retina: 2
---

# Color palette overview
All code is ready to go for `R`. To use the color palettes for displaying purposes in `Javascript` (GEE) or `Python`, simply copy-paste the lists beneath the example images.

```{r, message=FALSE}
library(RColorBrewer)
library(viridis)
library(wesanderson)
library(tidyverse)
library(cartography)

heatmap$value <- scale(heatmap$value)

plot <- function(pal){
  ggplot(heatmap, aes(x = X2, y = X1, fill = value)) +
    geom_tile() + 
    scale_fill_gradientn(colours = pal) + 
    scale_x_discrete(expand = c(0, 0)) +
    scale_y_discrete(expand = c(0, 0)) + 
    coord_equal() 
}
```
# Multi-color palettes
## Spectral 
```{r}
spectral <- brewer.pal(9, "Spectral")
plot(spectral)
```

```{js}
normal
["D53E4F", "F46D43", "FDAE61", "FEE08B", "FFFFBF", "E6F598", "ABDDA4", "66C2A5", "3288BD"]
reversed
["3288BD", "66C2A5", "ABDDA4", "E6F598", "FFFFBF", "FEE08B", "FDAE61", "F46D43", "D53E4F"]
```

## Viridis
```{r}
viridis <- viridis(9)
plot(viridis)
```

```{js}
normal
["440154", "472D7B", "3B528B", "2C728E", "21908C", "27AD81", "5DC863", "AADC32", "FDE725"]
reversed
["FDE725", "AADC32", "5DC863", "27AD81", "21908C", "2C728E", "3B528B", "472D7B", "440154"]
```

## Magma
```{r}
magma <- viridis(9, option = "magma")
plot(magma)
rev(magma)
```

```{js}
normal
["000004", "1D1147", "51127C", "822681", "B63679", "E65164", "FB8861", "FEC287", "FCFDBF"]
reversed
["FCFDBF", "FEC287", "FB8861", "E65164", "B63679", "822681", "51127C", "1D1147", "000004"]
```

## Plasma
```{r}
plasma <- viridis(n = 8, option = "plasma")
plot(plasma)
```

```{js}
normal
["0D0887", "4C02A1", "7E03A8", "A92395", "CC4678", "E56B5D", "F89441", "FDC328", "F0F921"]
reversed
["F0F921", "FDC328", "F89441", "E56B5D", "CC4678", "A92395", "7E03A8", "4C02A1", "0D0887"]
```

# Diverging palletes
## Red Blue
```{r}
RdBu <- brewer.pal(8, "RdBu")
plot(RdBu)
```

```{js}
normal
["B2182B", "D6604D","F4A582", "FDDBC7", "D1E5F0", "92C5DE", "4393C3", "2166AC"]
reversed
["2166AC", "4393C3", "92C5DE", "D1E5F0", "FDDBC7", "F4A582", "D6604D", "B2182B"]
```

## Yellow Green Blue
```{r}
YlGnBu <- brewer.pal(9, "YlGnBu")
plot(YlGnBu)
```

```{js}
normal
["FFFFD9", "EDF8B1", "C7E9B4", "7FCDBB", "41B6C4", "1D91C0", "225EA8", "253494", "081D58"]
reversed
["081D58", "253494", "225EA8", "1D91C0", "41B6C4", "7FCDBB", "C7E9B4", "EDF8B1", "FFFFD9"]
```

## Yellow Green 
```{r}
YlGn <- brewer.pal(9, "YlGn")
plot(YlGn)
rev(YlGn)
```

```{js}
normal
["FFFFE5", "F7FCB9", "D9F0A3", "ADDD8E", "78C679", "41AB5D", "238443", "006837", "004529"]
reversed
["004529", "006837", "238443", "41AB5D", "78C679", "ADDD8E", "D9F0A3", "F7FCB9", "FFFFE5"]
```

## Turquoise
```{r}
turquiose <- cartography::carto.pal(pal1 = "turquoise.pal", n1 = 9)
plot(turquiose)
```

```{js}
["B6EFB6", "A5D8B1", "95C2AC", "85ACA7", "7190A1", "5B739B", "435490", "253175", "080E5B"]
```

# Single color palettes
## Green
```{r}
Greens <- brewer.pal(9, "Greens")
plot(Greens)
```

```{js}
["F7FCF5", "E5F5E0", "C7E9C0", "A1D99B", "74C476", "41AB5D", "238B45", "006D2C", "00441B"]
```

## Blue
```{r}
Blues <- brewer.pal(9, "Blues")
plot(Blues)
```

```{js}
["F7FBFF", "DEEBF7", "C6DBEF", "9ECAE1", "6BAED6", "4292C6", "2171B5", "08519C", "08306B"]
```

## Red
```{r}
Reds <- brewer.pal(9, "Reds")
plot(Reds)
```

```{js}
["FFF5F0", "FEE0D2", "FCBBA1", "FC9272", "FB6A4A", "EF3B2C", "CB181D", "A50F15", "67000D"]
```

## Orange
```{r}
Orange <- cartography::carto.pal(pal1 = "orange.pal", n1 = 9)
plot(Orange)
```

```{js}
["FDE686", "FDD271", "FDBF5D", "FDAC49", "FE9430", "FE7B15", "FD5C00", "F82E00", "F40000"]
```

## Grey
```{r}
Grey <- cartography::carto.pal(pal1 = "grey.pal", n1 = 9)
plot(Grey)
```

```{js}
["DDDCDC", "C8C7C7", "B3B3B3", "9E9E9E", "858585", "696969", "4D4D4D" "2E2E2E", "10100F"]
```

# TV-inspired palettes
## Wes Anderson: The Life Aquatic with Steve Zissou (2004)
```{r}
zissou <- wes_palette("Zissou1")
plot(zissou)
```

```{js}
["3B9AB2", "78B7C5", "EBCC2A", "E1AF00", "F21A00"]
```


# Further color resources
- [Summary of almost all available R color packages](https://github.com/EmilHvitfeldt/r-color-palettes)
- [Adobe color wheel](https://color.adobe.com/)

